k-plus Anticlustering: An Improved k-means Criterion for Maximizing Between-Group Similarity

### 2024-02-01 paper.Rmd
minor

Traditionally, assigning stimuli to experimental conditions was done manually [e.g., @schaper2019metamory] or randomly [e.g., @kroneisen2018], both of which methods do not guarantee that the stimulus sets will be similar [@papenberg2020; @cutler1981; @vancasteren2007; @armstrong2012]. Generally, automated approaches are preferred that quantify similarity on the basis of the stimulus features and use an algorithm to assign stimuli in such a way that this similarity is optimized [@brusco2019; @papenberg2020].

>>>>

Traditionally, assigning stimuli to experimental conditions was done manually [e.g., @schaper2019metamory] or randomly [e.g., @kroneisen2018], both of which methods however do not ensure that the stimulus sets will be similar [@papenberg2020; @cutler1981; @vancasteren2007; @armstrong2012]. Generally, automated approaches are preferred that quantify similarity on the basis of the stimulus features and use an algorithm to assign stimuli in such a way that this similarity is optimized [@brusco2019; @papenberg2020]. One approach that has recently gained traction
